### 2019-03-18 README.Rmd
Fix yaml

[![Created by EcoHealth Alliance](https://raw.githubusercontent.com/ecohealthalliance/citesdb/master/man/figures/eha-footer.png)](https://www.ecohealthalliance.org/)

>>>>

[![Created by EcoHealth Alliance](https://raw.githubusercontent.com/ecohealthalliance/citesdb/master/man/figures/eha-footer.png){data-external="1"}](https://www.ecohealthalliance.org/)
